%1-25 rework:
Over the course of this three-year project, Mankoff and Caspi, partnering with the Taskar Center for Accessible Technology (which Caspi directs), will create Tactile Map Tiles, a navigation solution that lets Deaf-blind individuals easily create custom, 3-D printable tactile maps that meet their diverse navigation and transportation needs. No current technology or apps communicate information about the layout of an environment in a manner that is easily and portably consumable by this cohort. As a result, this dual sensory loss population suffers from significant barriers to economic participation and problems attendant to social isolation.
Challenging the existing primacy afforded to vision, this work takes a tactile approach. We will focus our design on a scalable, cost-efficient 3-D printing solution that makes use of the most current pedestrian-centric information and standard tactile symbols. Newly designed optimizations will let us express more types of information in less tactile map real estate and permit Deaf-blind users to specify their own travel needs and preferences, such as area and type of travel and requirements regarding gradation. Our participatory design process will encourage members of the Deaf-blind community to strongly voice their preferences for the design of accessible interfaces, which we will seamlessly integrate with our own highly regarded AccessMap route-finding service. All user-initiated exchanges will make use of a 14 cell portable Braille reader, the most constrained interface now in use.
Expected product outcomes include an algorithm for creating custom maps, an accessible interface for specifying customization parameters, and an optional, email-based notification system to keep users abreast of changes to the landscape and the services in a specified travel area. Using Tactile Map Tiles, Deaf-blind pedestrians will finally be able to access current, relevant, pedestrian-centric digital map and transit information. By doing so, they will become more self-reliant travelers and more socially and economically connected members of society.


%Over the course of this three-year project, Mankoff and Caspi, partnering with Caspi's Taskar Center for Accessible Technology, \jm{XXAnat: other partners??} will create a navigation solution that lets Deaf-blind 
%individuals easily create custom, 3-D printable maps that meet their diverse needs. Our \textbf{goal} is to provide unprecedented access for Deaf-blind people to the most currently available digital mapping and transit information and offer these individuals the independent ability to create their own maps.  Specific \textbf{objectives} are to: 1) extend the AccessMap interface to support need and route specification, 2) automatically optimize map design based on specific user needs, and 3) connect map production to existing online printing services. Anticipated \textbf{outcomes} include: 1) the ability of Deaf-blind individuals and those supporting them to independently create custom maps, 2) significant improvements to the navigational experience of this cohort that impose no cost and time requirements that exceed those already imposed by existing services, and 3) a solution that is seemlessly integrated into the well-received AccessMap infrastructure. Expected \textbf{product} outcomes include an algorithm for creating custom maps, an accessible interface for specifying customization parameters, and software for AccessMap integration. 
