Our product will enable Deaf-blind individuals and those who support them  to independently create custom maps. Our studies will help support iterative design as we  refine and improve this product over the course of the proposal.

\subsubsection{Study 1: Usability of Interface Extensions}
Our first study will demonstrate the basic usability and accessibility of the updated AccessMap Interface. Specifically, we will test four specific tasks: Creating an account; Searching for an address; Setting Personalization Parameters, and Generating a map; Generating a map of choice.

\paragraph{Sample} For this sample, we will recruit Deaf-blind individuals, since the accessibility of the system to that specific population is a necessary precondition for the impact of our product. 

\paragraph{Environment} This study will take place in a lab environment, since our focus is on ensuring basic usability.

\paragraph{Test Trials}
After being introduced to the study, participants will be asked to use a modified think-aloud protocol while using AccessMap to accomplish each of the tasks. Because the study will involve Deaf-blind participants, participants will be instructed to complete each task, pausing to communicate with us if they have questions or comments about the interface. The entire session will be video-recorded, and an interpreter will be present to support communication between participants and the experimenters. At the end of the study, participants will be given a brief survey to fill out where they can add further comments about their experience. 

The final task, Generating a map of choice, will be participants' opportunity to generate a map for a location of their choice that they would like to use. This map will be printed and mailed to participants for the final study, end-to-end system use, described below. 

\subsubsection{Study 2: End-to-end system use}
\label{sec:field-web}
\jm{test that they can produce a map on their own when they want and use it}
The goal of the final study is to see how participants use the system to independently generate and use maps. 

\paragraph{Sample}
This study will involve the same sample as the previous study: Deaf-blind individuals local to our University. In addition, we will advertise the study in all cities where AccessMap data exists \jm{xx anat: list of cities}. This will help to expand our sample. 

\paragraph{Environment}
This study will take place online. Participants will be asked to fill out a survey the first and second time they use Accessmap. In addition, with their permission, we will log all interactions with the system.  Lastly, we will interview participants about their experience, and what happened when they received the physical map they requested (including how they used it and whether they used it). 