\label{sec:workplan}

Link this back to the Proof of Concept and Proof of Product discussions above. 
Name the specific Work Products of each and milestones. Give final Gantt chart.

The Work Plan should cover all three (3) years of the project period. The Work Plan should include a statement of the project's overall goal(s), anticipated outcome(s), and the major tasks that are proposed to achieve the goal and outcome(s). For each major task, the work plan should identify timeframes involved and the lead person responsible for the task.

NOTE : Applicants requesting funding for a multi-year grant program are REQUIRED to provide a Project Work Plan for EACH potential year of grant funding requested.
Goal:


This project includes both the \textit{proof of concept} stage and the \textit{proof of product} stage:
\begin{description}
\item Week 1 - Proof of Concept Phase Start. 
\item Week 2-3 - Send out Early Development Baseline Survey (see Section \ref{test:baseline}).
\item Week 2-12 - Develop Automated Pipeline for Tactile Map Model production (See Section \ref{sec:fabrication}).
\item Week 5-75 - Develop Optimization Algorithms for Tactile Map Model production (See Section \ref{sec:optimize})
\item Week 25-27 Technical and validation testing (for alpha, Milestone 1)
\item Week 27 - Milestone 1: Exploration based map generation complete (no web interface)
\item Week 28-30 - Alpha user field tests and Alpha user surveys
\item Week 50-70 Testing Optimization Algorithm
\item Week 75 - Milestone 2: Itinerary or Route-Based Tactile Map Planning.
\item Week 85 - Milestone 3: Transit Service Feed support, Transit-Based Trip Planning on Tactile Map.
\item Week 95-100 Technical and validation testing (for beta, Milestone 4)
\item Week 100 - Milestone 4: Full AccessMap Integration, Advanced Transit Mapping (Beta)
\item Week 100 – Proof of Product, Phase II Start. 
\item Week 102-108 - Extend UI Functionality responding to Stakeholder Input
\item Week 110-113 - Testing in Natural Contexts, Beta Field Demonstration start.
\item Week 112-118 - Extend UI Functionality responding to Beta Stakeholder Input
\item Week 150 – Project Close and Report.

\end{description}

Measurable Outcome(s):
* Time Frame (Start/End Dates by Month in Project Cycle)

% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{table}[h]
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}p{3cm}p{4cm}p{2cm}llllllllllll@{}}
\rowcolor[HTML]{333333} 
{\color[HTML]{FFFFFF} \textbf{Major Objectives}} & {\color[HTML]{FFFFFF} \textbf{Key Tasks}} & {\color[HTML]{FFFFFF} \textbf{Lead Person}} & {\color[HTML]{FFFFFF} \textbf{Q1}} & {\color[HTML]{FFFFFF} \textbf{Q2}} & {\color[HTML]{FFFFFF} \textbf{Q3}} & {\color[HTML]{FFFFFF} \textbf{Q4}} & {\color[HTML]{FFFFFF} \textbf{Q5}} & {\color[HTML]{FFFFFF} \textbf{Q6}} & {\color[HTML]{FFFFFF} \textbf{Q7}} & {\color[HTML]{FFFFFF} \textbf{Q8}} & {\color[HTML]{FFFFFF} \textbf{Q9}} & {\color[HTML]{FFFFFF} \textbf{Q10}} & {\color[HTML]{FFFFFF} \textbf{Q11}} & {\color[HTML]{FFFFFF} \textbf{Q12}} \\ 
1. Map Creation & Define Objective Function  & Mankoff/ Caspi & XX & XX &XX  & XX &  &  &  &  &  &  &  &  \\
 & Survey Users to determine Information Importance & XX &XX  &  &  &  &  &  &  &  &  &  &  &  \\
 & Simulate use to determine Attentive Cost & XX &XX  & XX  &  &  &  &  &  &  &  &  &  &  \\
  & Map Understanding (Study 1) &  &  & XX & XX &  &  &  &  &  &  &  &  &  \\
   & Technical Validation (Study 2) &  &  & XX  & XX &  &  &  &  &  &  &  &  &  \\
    & Navigation Benefits (Study 3) &  &  & XX & XX &XX  &  &  &  &  &  &  &  &  \\
 2. &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ \bottomrule
\end{tabular}%
}
\end{table}